### 2017-05-07 2017mergingmerges/section/XX-Related.tex
Cite sync kahn networks

Synchronous languages such as LUSTRE~\cite{halbwachs1991synchronous}, Lucy-n~\cite{mandel2010lucy} and SIGNAL~\cite{le2003polychrony} all use some form of clock calculus and causality analysis to ensure that programs can be statically scheduled with bounded buffers. These languages describe \emph{passive} processes where values are fed in to streams from outside environments, such as data coming from sensors. In contrast, our processes are \emph{active} and have control over when data is pulled from the source streams, which is nessesary for multiple input combinators such as @merge@ and  @append@.

>>>>

Synchronous languages such as LUSTRE~\cite{halbwachs1991synchronous}, Lucy-n~\cite{mandel2010lucy} and SIGNAL~\cite{le2003polychrony} all use some form of clock calculus and causality analysis to ensure that programs can be statically scheduled with bounded buffers~\cite{caspi1996:kahn}. These languages describe \emph{passive} processes where values are fed in to streams from outside environments, such as data coming from sensors. In contrast, our processes are \emph{active} and have control over when data is pulled from the source streams, which is nessesary for multiple input combinators such as @merge@ and  @append@.
Synchronous dataflow languages reject operators with value dependent control flow such as @merge@, while general dataflow languages fall back on less performant dynamic scheduling \cite{bouakaz2013real}.
